---
title: "fireSense_EscapeFit"
author: "Jean Marchal (jean.d.marchal@gmail.com)"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  html_document: default
  pdf_document: default
---

# Overview
Fit statistical models that can be used to parameterize the fire escape component of landscape fire models (e.g. fireSense).

# Download the module
```{r download module, eval = FALSE, echo = TRUE}
library(SpaDES)

moduleName <- "fireSense_EscapeFit"

spadesModulesDirectory <- tempdir() # Location where the module will be downloaded

downloadModule(moduleName, path = spadesModulesDirectory)
```

# Usage
## Module parameters
Name|Default|Description
----|:--------------|---------------------------------------------------------------------
`formula`|`NA`|a formula describing the model to be fitted.
`data`|`"dataFireSense_EscapeFit"`|a character vector indicating the names of objects in the `simList` environment in which to look for variables present in the model formula. `data` objects should be data.frames.
`.runInitialTime`|`start(simList)`|when to start this module? By default, the start time of the simulation.
`.runInterval`|`NA`|optional. Interval between two runs of this module, expressed in units of simulation time.
`.saveInitialTime`|`NA`|optional. When to start saving output to a file.
`.saveInterval`|`NA`|optional. Interval between save events.
|||



## Usage example
```{r module usage example, eval = FALSE}
library(SpaDES)

spadesModulesDirectory <- ".."

# Define simulation parameters
times <- list(start = 1, end = 1, timeunit = "year")
modules <- list("fireSense_EscapeFit")
paths <- list(
  modulePath = spadesModulesDirectory
)

# Example of model formula with piecewise terms
model <- escaped ~ MonthlyDroughtCode_July + PcHardwood + PcConifer + PcDisturbed + PcOther + PcWater

# Define module parameters
parameters <- list(
  fireSense_EscapeFit = list(
    formula = formula,
    data = "dataFireSense_EscapeFit"
  )
)

# Define from where and how data will be loaded in the simList environment
inputs <- data.frame(
  objectName = "dataFireSense_EscapeFit",
  file = "/path/to/data/input/",
  fun = "readRDS",
  package = "base",
  loadTime = 1
)

# Create the simList
sim <- simInit(
  times = times,
  modules = modules,
  params = parameters,
  paths = paths,
  inputs = inputs
)

sim <- spades(sim)
sim$fireSense_EscapeFitted
```

# Events
Events are scheduled as follows:

- Module initialisation
- Model fitting

# Data dependencies
## Input data
- **dataFireSense_EscapeFit**: one or more data.frames in which to look for variables present in the model formula.

## Output data
- **fireSense_EscapeFitted**: an object of class `fireSense_EscapeFit`, inherited from the class `glm`.

# Links to other modules
This model can be used to parameterize the fire escape component of landscape fire models such as fireSense.

